Study Level trends

### 2024-10-14 analysis/06_study_change.Rmd
Look at CWM changes for each study

>>>>

Look at CWM's
```{r}
cwm_counts <- model_output %>% 
  filter(!is.na(study_id), model_id == "base", p.adjust < 0.05, 
         !metric %in% c("S", "FRic", "FEve", "FDiv", "SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_base")) %>% 
  select(metric, study_id) %>% 
  count(metric)

# get study-level significant CWM counts with their other change characteristics
cwm_counts %>% 
  full_join(change_groups) %>% 
  select(-c("FRic", "FEve", "FDiv")) %>% 
  View()
```
